---
title: "Linear"
author: "Lucia Wang"
date: "2023-11-09"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
library(tidyverse)
library(p8105.datasets)

set.seed(1)
```
## Linear models
Import + tidy nyc airbnb data
```{r}
data("nyc_airbnb") 

nyc_airbnb = nyc_airbnb |>
  mutate(stars = review_scores_location / 2) |>
  select(
    price, stars, borough=neighbourhood_group, neighbourhood, room_type
  ) |>
  filter(borough != "Staten Island")
```

Let's fit a model
```{r}
fit = 
  nyc_airbnb |>
  lm(price ~ stars + borough, data= _) # since we piped it in, we use data= _ 
```

Let's look at it!
`broom` package has lots of functions for summary or cleaning table
```{r}
fit

summary(fit) # matrix
summary(fit)$coef # look at just coeffs
coef(fit) # pulls out that table
# fitted.values(fit) # all the fitted values - big table

fit |> broom::glance()
fit |> broom::tidy() #gives a tibble

fit |> broom::tidy() |>
  mutate(term= str_replace(term, "^borough", "Borough: ")) |>
  select(term, estimate, p.value) |>
  knitr::kable(digits=3)
```

## Diagnostics
you can add residuals or fitted values to the df
```{r}
nyc_airbnb |>
  modelr::add_residuals(fit)

nyc_airbnb |> modelr::add_predictions(fit)

nyc_airbnb |> 
  modelr::add_residuals(fit) |> 
  ggplot(aes(x = borough, y = resid)) + geom_violin()
```

## Anova
test means between groups
```{r}
fit_null = lm(price ~ stars + borough, data = nyc_airbnb)
fit_alt = lm(price ~ stars + borough + room_type, data = nyc_airbnb)

anova(fit_null, fit_alt) |> 
  broom::tidy()
```

what about borough level differences (interaction)
```{r}
fit = 
  nyc_airbnb |>
  lm(price ~ stars*borough + room_type*borough, data= _)
```

This works but takes a while/ hard to understand. Instead, nest within the boroughs
```{r}
airbnb_lm = function(df) {
  lm(price ~ stars + room_type, data=df)
}

nyc_airbnb |>
  nest(df= -borough) |>
  mutate(models = map(df, airbnb_lm),
         results = map(models, broom::tidy))  |>
  select(borough, results) |>
  unnest(results) |>
  select(borough, term, estimate) |>
  pivot_wider(names_from = term,
              values_from = estimate) |>
  knitr::kable(digits=2)
```

you can create an anonymous function too using`\(df)` then defining it there

## Binary outcomes
```{r}

```

